\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%\documentclass[ALICE,manyauthors]{ALICE_scientific_notes}
%
\usepackage{lineno}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{makeidx}
\usepackage{color}
\usepackage{color}
\pagestyle{headings}
\usepackage{epstopdf}
\usepackage[normalem]{ulem}
\usepackage{afterpage}
\usepackage{tabularx,booktabs}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{hyperref} 
\usepackage{enumitem}
\usepackage{braket}
\usepackage{here}
\usepackage[utf8]{inputenc}
\usepackage[noadjust]{cite}

\setlist[description]{%
  topsep=5pt,               % space before start / after end of list
  itemsep=5pt,               % space between items
  %font={\bfseries\sffamily}, % set the label font
  font={\bfseries\sffamily\color{blue}}, % if colour is needed
  before={\color{blue!60!red}\itshape}
}

%%%
%%%  Alias
%%%

\makeatletter
    \setlength\@fptop{0\p@}
\makeatother

\input{commands.tex}

%%%
%%% end Alias
%%%

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[backend=biber,backref=false,
%sorting=none,style=numeric,
%isbn=false,doi=false,hyperref=true,
%url=false,eprint=true,firstinits=true]{biblatex}
%%%%% you can add multiple bib files containing your refrences %%%%%%%%%%%%
%\addbibresource{refer.bib}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[square,numbers,sort&compress]{natbib}

\begin{document}
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%

\begin{titlepage}
%
\PHnumber{ALICE-2020-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{ Inclusive and multiplicity dependent production of electrons from heavy-flavour hadron decays in pp and \pPb collisions}
%\ShortTitle{}   
\ShortTitle{electrons from heavy-flavour hadron decays in pp and \pPb collisions.}
% appears on right page headers
%
%\author{Authors list to be filled}
%\Collaboration{ Authors list to be filled }%
\author{ALICE Collaboration$^{*}$}
\ShortAuthor{ALICE Analysis Note 2017} % appears on left page headers, do not change
%
\begin{abstract}

Heavy-flavour production at midrapidity is studied using electrons from heavy-flavour hadron decays in pp collisions at $\sqrt{s}=13$ TeV to precisely test perturbative QCD calculations, and to study effects from cold nuclear matter (CNM) in \pPb collisions at $\sqrt{s_{\rm{NN}}} = 8.16$ TeV. Furthermore, their production in-terms of self-normalized yield as a function of normalized charged-particle multiplicity, estimated at midrapidity, in pp and \pPb collisions is studied to investigate the role of multiple-parton interactions (MPI) and the interplay between hard and soft mechanism in particle production. The production cross section of electrons from heavy-flavour hadron decays measured in the transverse momentum (\pt) range from $0.2$ $< p_{\rm T} <$ $35$ GeV$/c$ in pp collisions at $\sqrt{s}=13$ TeV is compared with pQCD calculation. The nuclear modification factor of electrons from heavy-flavour hadron decays measured as a function of \pt in \pPb collisions at $\sqrt{s_{\rm{NN}}} = 8.16$ TeV in the range 0.5 $< p_{\rm T} <$ 26 GeV/$c$, is consistent with unity within the statistical and systematic uncertainties. The self-normalized yield in pp and \pPb collisions grows faster than linear with the normalized multiplicity. In pp collisions a strong \pt dependence is observed, where the yield of higher \pt electrons increases faster as a function of multiplicity compared to the one of lower \pt electron. The measurement in \pPb collisions shows a weaker \pt dependence within uncertainties. The self-normalized yield in pp collisions is compared with PYTHIA 8.2 Monte-Carlo simulations and with measurements of inclusive charged particles, D-mesons and J/$\psi$. In \pPb collisions, the self-normalized yield as a function of normalized charged-particle multiplicity is compared with D-mesons measurements. 

%Heavy-flavour production studies in pp collisions, besides providing the necessary baseline for measurements in \PbPb collisions, constitute a precision test of perturbative QCD calculations. In complex systems such as \pPb collisions, it gives insights into the cold nuclear matter (CNM) effects. Furthermore, their production as a function of charged-particle multiplicity in pp and \pPb collisions provides insights into the role of multiple-parton interactions (MPI) and the interplay between hard and soft mechanism in particle production. In \pPb collisions, the production is also influenced by the concurrent multiple binary nucleon-nucleon collisions. 
%In this paper, we will present the measurement of the yield of electrons from heavy-flavour hadron decays at midrapidity as a function of the transverse momentum and charged-particle multiplicity estimated at midrapidity (self-normalized yield) in pp collisions at \sqrts = 13 TeV and in \pPb collisions at \sqrtsNN = 8.16 \TeV.
\\
\\
{\it Keywords:} Heavy-flavour electrons, nuclear modification factor, self-normalized yield, multiplicity, pp collisions, \pPb collisions

\end{abstract}
\end{titlepage}
\input{introduction.tex}
\input{datasampleandselection.tex}
\input{multiplicityanalysis.tex}
\input{heavyflavour.tex}
\input{corrections.tex}
\input{systematics.tex}
%\input{ppReference.tex}
\input{results.tex}
%\input{ModelComparison.tex}
\input{Conclusion.tex}

\clearpage
\input{Acknowledgement.tex}

\clearpage

\bibliographystyle{utphys}   % Remember we use title in the biblio
\bibliography{bibliography.bib}

%\bibliography{./bib/AlicePaper2016,./bib/ref_corrections,./bib/ref_d0reconstructionandselections,./bib/ref_datasampleandselection,./bib/ref_eventshapedefinitions,./bib/ref_experimentalsetup,./bib/ref_multiplicitydefinitions,./bib/ref_introduction,./bib/ref_systematics,biblio}


\end{document}
